---
title: "BAN 502 PowerPoint"
author: "Zackery Bradley"
date: "9/17/2021"
output:
  ioslides_presentation: default
  slidy_presentation: default
  powerpoint_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
**Packages**
```{r}
library(flexdashboard)
library(tidyverse)
library(ggplot2)
library(tidymodels)
library(vip)
train_fit = readRDS("train_fit.rds")
test = readRDS("test.rds")
train = readRDS("train.rds")
 student_split = readRDS("student_split.rds")
student = readRDS("student.rds")
```
library(flexdashboard)
library(tidyverse)
library(ggplot2)
library(tidymodels)
train_fit = readRDS("train_fit.rds")
rsconnect::deployApp('path/to/your/app')
**Glimpse**
```{r}
glimpse(train)
```


**Slide 1**
Title" A Market Evaluation of homes in Ames Iowa
Representation by: Zackery Bradley

**Important factors in home values**
```{r slide 2}

train_fit %>% pull_workflow_fit() %>% vip(geom = "point")

```


## Slide 3 with Bullets

- From our market analysis, this chart serves as a representation of what variables drive the market price of homes in Ames, Iowa. 
- we can see that the most important factors in home pricing is square footage, year built, and the number of cars that can be stored in the garage
- Below is further analysis pinpointing these three factors' importance in our target market. 

## Slide with R Output

```{r slide 4}
ggplot(train, aes(x = Gr_Liv_Area, y = Above_Median)) + geom_boxplot()+ggtitle("Ames Iowa Homes")
```

## Slide with Plot

```{r slide 5}
ggplot(train, aes(x = Garage_Cars , fill = Above_Median)) + geom_bar(position = "fill")+ggtitle("Ames Iowa Homes")
```

```{r slide 6}
ggplot(train, aes(x = Year_Built, y = Above_Median)) + geom_boxplot()+ggtitle("Ames Iowa Homes")
```
**Suggestions for our targets (slide 7)**
-We should focus on building new homes rather than renovating existing ones
-The bigger, the better! Lets focus on designing our homes to have the least "wasted space" available, thus maximizing our square footage
-We should prioritize having more garage space than our competitors 

