---
title: "BAN 502 Project"
author: "Zackery Bradley"
date: "9/14/2021"
output: word_document
---



**Packages and Datasets**
```{r}

rsconnect::setAccountInfo(name='zackerybradley', token='17424B895B53A2576DA270EC5DEAE3CF', secret='tzIoTmQDagLMQIDz4EJ5ss4HgqtAu+1Xws43B1h/')
library(rsconnect)


library(tidyverse)
library(tidymodels)
library(ranger)
library(VIM) 		
library(rpart) 			
library(rpart.plot) 			
library(RColorBrewer)
library(caret)
library(mlbench)
library(dplyr)
library(ggrepel)
library(naniar)
library(vip)
library(ggplot2)

#competition = read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 5/ames_competition.csv")

student = read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 5/ames_student.csv")
#sampleSubmission = read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 5/sampleSubmission.csv")
```

library(tidyverse)
library(tidymodels)
library(ranger)
library(VIM) 		
library(rpart) 			
library(rpart.plot) 			
library(RColorBrewer)
library(caret)
library(mlbench)
library(dplyr)
library(ggrepel)
library(naniar)
library(vip)
library(ggplot2)


#competition = read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 5/ames_competition.csv")

student = read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 5/ames_student.csv")
#sampleSubmission = read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 5/sampleSubmission.csv")
**Identifying Missing Data**
```{r}
student = student %>% mutate_if(is.character,as_factor)
student = student %>% mutate(Above_Median = as_factor(Above_Median)) %>%
  mutate(Above_Median = fct_recode(Above_Median, "No" = "0", "Yes" = "1"))

vis_miss(student)

```



**Split**

```{r}
set.seed(1234)
student_split = initial_split(student, prob = .70, strata = Above_Median)
train = training(student_split)
test = testing(student_split)
 
```

**visualizations**
```{r}
#summary(train)


p1 = ggplot(train, aes(x = MS_SubClass , fill = Above_Median)) + geom_bar(position = "fill")
theme(axis.text.x = element_text(angle = 90, vjust=0.9)) 
p2 = ggplot(train, aes(x = MS_Zoning, fill = Above_Median)) + geom_bar(position = "fill")
p3 =  ggplot(train, aes(x = Street, fill = Above_Median)) + geom_bar(position = "fill") 
p4 =  ggplot(train, aes(x = Alley, fill = Above_Median)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
p1 = ggplot(train, aes(x = Lot_Shape, fill = Above_Median)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = Land_Contour, fill = Above_Median)) + geom_bar(position = "fill")
theme(axis.text.x = element_text(angle = 90, vjust=0.5))
p3 =  ggplot(train, aes(x = Utilities, fill = Above_Median)) + geom_bar(position = "fill")
p4 =  ggplot(train, aes(x = Lot_Config, fill = Above_Median)) + geom_bar(position = "fill")
theme(axis.text.x = element_text(angle = 90, vjust=0.5))
grid.arrange(p1,p2,p3,p4)
p1 = ggplot(train, aes(x = Land_Slope, fill = Above_Median)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = Neighborhood, fill = Above_Median)) + geom_bar(position = "fill")
p3 =  ggplot(train, aes(x = Condition_1, fill = Above_Median)) + geom_bar(position = "fill")
p4 =  ggplot(train, aes(x = Condition_2, fill = Above_Median)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
p1 = ggplot(train, aes(x = Bldg_Type, fill = Above_Median)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = House_Style, fill = Above_Median)) + geom_bar(position = "fill")
p3 =  ggplot(train, aes(x = Overall_Qual, fill = Above_Median)) + geom_bar(position = "fill")
p4 =  ggplot(train, aes(x = Overall_Cond, fill = Above_Median)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
p1 = ggplot(train, aes(x = Roof_Style, fill = Above_Median)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = Roof_Matl, fill = Above_Median)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = Exterior_1st, fill = Above_Median)) + geom_bar(position = "fill")
p4 =  ggplot(train, aes(x = Exterior_2nd, fill = Above_Median)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
p1 =  ggplot(train, aes(x = Mas_Vnr_Type, fill = Above_Median)) + geom_bar(position = "fill")
p2 =  ggplot(train, aes(x = Mas_Vnr_Area, fill = Above_Median)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = Exter_Qual, fill = Above_Median)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = Exter_Cond, fill = Above_Median)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
p1 =  ggplot(train, aes(x = Foundation, fill = Above_Median)) + geom_bar(position = "fill")
p2 =  ggplot(train, aes(x = Bsmt_Qual, fill = Above_Median)) + geom_bar(position = "fill")
p3 =  ggplot(train, aes(x = Bsmt_Cond, fill = Above_Median)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = Bsmt_Exposure, fill = Above_Median)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
p1 = ggplot(train, aes(x = BsmtFin_Type_1, fill = Above_Median)) + geom_bar(position = "fill")
p2 =  ggplot(train, aes(x = BsmtFin_Type_2, fill = Above_Median)) + geom_bar(position = "fill")
p3 =  ggplot(train, aes(x = Heating, fill = Above_Median)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = Heating_QC, fill = Above_Median)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
p1 = ggplot(train, aes(x = Central_Air, fill = Above_Median)) + geom_bar(position = "fill")
p2 =  ggplot(train, aes(x = Electrical, fill = Above_Median)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = Garage_Cars , fill = Above_Median)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3)

p1 = ggplot(train, aes(x = Lot_Frontage, y = Above_Median)) + geom_boxplot()
p2 = ggplot(train, aes(x = Lot_Area, y = Above_Median)) + geom_boxplot()
p3 = ggplot(train, aes(x = Year_Built, y = Above_Median)) + geom_boxplot()
p4 = ggplot(train, aes(x = Year_Remod_Add, y = Above_Median)) + geom_boxplot()
grid.arrange(p1,p2,p3,p4, ncol = 2)
p1 = ggplot(train, aes(x = Mas_Vnr_Area, y = Above_Median)) + geom_boxplot()
p2 = ggplot(train, aes(x = BsmtFin_SF_1, y = Above_Median)) + geom_boxplot()
p3 = ggplot(train, aes(x = BsmtFin_SF_2, y = Above_Median)) + geom_boxplot()
p4 = ggplot(train, aes(x = Bsmt_Unf_SF, y = Above_Median)) + geom_boxplot()
grid.arrange(p1,p2,p3,p4, ncol = 2)
p1 = ggplot(train, aes(x = Total_Bsmt_SF, y = Above_Median)) + geom_boxplot()
p2 = ggplot(train, aes(x = First_Flr_SF, y = Above_Median)) + geom_boxplot()
p3 = ggplot(train, aes(x = Second_Flr_SF, y = Above_Median)) + geom_boxplot()
p4 = ggplot(train, aes(x = Low_Qual_Fin_SF, y = Above_Median)) + geom_boxplot()
grid.arrange(p1,p2,p3,p4, ncol = 2)
p1 = ggplot(train, aes(x = Gr_Liv_Area, y = Above_Median)) + geom_boxplot()
p2 = ggplot(train, aes(x = Bsmt_Full_Bath, y = Above_Median)) + geom_boxplot()
p3 = ggplot(train, aes(x = Bsmt_Half_Bath, y = Above_Median)) + geom_boxplot()
p4 = ggplot(train, aes(x = Full_Bath, y = Above_Median)) + geom_boxplot()
grid.arrange(p1,p2,p3,p4, ncol = 2)





```







**Random Forest 1**
```{r}

train_recipe = recipe(Above_Median ~., train) %>%
  step_dummy(all_nominal(), -all_outcomes())

train_model = rand_forest() %>% 
  set_engine("ranger", importance = "permutation") %>% 
  set_mode("classification")

train_wflow = 
  workflow() %>% 
  add_model(train_model) %>% 
  add_recipe(train_recipe)

set.seed(12345)
train_fit = fit(train_wflow, train)

```

**variable importance**
```{r}
train_fit %>% pull_workflow_fit() %>% vip(geom = "point")
```

**Phase 2 ideas**
```{r}
trainpredrf = predict(train_fit, train)
head(trainpredrf)


confusionMatrix(trainpredrf$.pred_class, train$Above_Median, 
                positive = "Yes")
```


**load and save**
```{r}
saveRDS(train_fit, "train_fit.rds")
train_fit = readRDS("train_fit.rds")
saveRDS(train_fit, "test.rds")
train_fit = readRDS("test.rds")
saveRDS(train_fit, "train.rds")
train_fit = readRDS("train.rds")
saveRDS(train_fit, "student.rds")
train_fit = readRDS("student.rds")
saveRDS(train_fit, "student_split.rds")
train_fit = readRDS("student_split.rds")
```



