---
output:
  word_document: default
  html_document: default
---
# **Module 3 - Assignment 1**
## **Bradley, Zackery**
### **Data Visualization**

#I will be using the datasets containing candy rasnkings and prodution. These datasets can be found in canvas.
```{r Packages}
library(tidyverse)
candy_data_1_<- read_csv("candy_data_1_.csv")
candy_production <- read_csv("candy_production.csv")
```
#== Part 2

#### **Visualization with Scatterplots (geom_point)**
```{r}
ggplot(data=candy_data_1_,aes(x= sugarpercent, y = pricepercent, label = competitorname))+
geom_point()+
geom_smooth(method ="lm")+
geom_text(check_overlap = T, 
vjust = "bottom", 
nudge_y = 0.01, 
angle = 30,
size = 2)+
labs(title ="Sugar by Price Scatterplot",
x = "Sugar content (percentile)", 
y = "Price (percentile)" 
 )
```
summary(candy_data_1_)

#the candy with the lowest price and highest sugar content is "Dum Dums". The candy with the highest price and highest sugar content is "milkyway simply caramel".
#== part 3

#### **Line Chart of Candy Production**

#we will be displaying a line chart showing the candy production for specific date and how production during that month is compared to 2012
```{r line chart}
ggplot(data = candy_production,aes(x=observation_date,y=IPG3113N, group=1))+
geom_line()+
geom_smooth(method =)+
labs(title ="Monthly Candy Production",
x = "Year", 
y = "As Percent of 2012 Production")
```


#==Part 4

#### **Bar Chart of Ingredients**
```{r Bar Chart}
ggplot(data = candy_data_1_, aes(chocolate))+
geom_bar()
candyFeatures <-candy_data %>% select(2:10)
candyFeatures[] <-lapply(candyFeatures,as.logical)
ggplot(data = candyFeatures, aes(chocolate))+
geom_bar()
```


