---
output:
  word_document: default
  html_document: default
---
#  Module 2 - Assignment 2
## Bradley, Zackery
### Introduction to R Markdown

#==Question  2
#This document will represent practicing with R markdown. Previously, we learned about Vectors, as well as learning about how different data types are written.this\will be the first time I have ever practiced with R Markdown.

#==question 3
#In this document, we will be revisiting some of the material from Module 1 Assignment 2, which will include a basic plot showing sales over the last six months. We are inserting this by creating a Chunk. Chunks can be used as a means to render output such as plots.

```{r Plot Of Sales by Month}
library(tidyverse)
```
  #==Question 11
#Reflecting back on Module 1, assignment 2, we recorded the largest sales month by selling a total of 300 in month 5.
  
  #==Question 12
```{r Working with Data Frames}
Yearly_Sales <- data.frame(Month = c("JAN","FEB","MAR","APR","MAY","JUNE","JULY","AUG","SEPT","OCT","NOV","DEC"),
Sales = c(150.25,258.4,268.55,122.52,987,458.82,667.23,845.54,586.78,888.58,756.12,456.84))
```
#==Question 15
#In module 1 assignment 2, we determined that May had the most sales, while the month of April had the least,

