---
title: "MOD 2 ASSIGNMENT 2"
author: "Zackery Bradley"
date: "9/1/2021"
output: word_document
---

```{r}
library(tidyverse)
library(tidymodels)
#install.packages("glmnet")
library(glmnet)
library(GGally)
#install.packages("ggcorrplot")
library(ggcorrplot)
library(MASS)
#install.packages("car")
library(car)
library(lubridate)
library(lmtest)
library(readr)
#install.packages("devtools")
library(devtools)
 #install_version("parsnip", version = "0.1.5", repos = "http://cran.us.r-project.org")
 library(parsnip)
bike_cleaned <- read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 2/bike_cleaned.csv")
```
library(tidyverse)
library(tidymodels)
install.packages("glmnet")
library(glmnet)
library(GGally)
install.packages("ggcorrplot")
library(ggcorrplot)
library(MASS)
install.packages("car")
library(car)
library(lubridate)
library(lmtest)
library(readr)
install.packages(“devtools”)
library(devtools)
 install_version("parsnip", version = "0.1.5", repos = "http://cran.us.r-project.org")
 library(parsnip)
bike_cleaned <- read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 2/bike_cleaned.csv")

**Task 1**

```{r}
bike_cleaned <- read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 2/bike_cleaned.csv")


bike = bike_cleaned %>% mutate(dteday =mdy(dteday)) 
bike = bike %>% mutate(season = as_factor(season))
bike = bike %>% mutate(mnth = as_factor(mnth))
bike = bike %>% mutate(holiday = as_factor(holiday))
bike = bike %>% mutate(weekday = as_factor(weekday))
bike = bike %>% mutate(workingday = as_factor(workingday))
bike = bike %>% mutate(weathersit = as_factor(weathersit))

bike = bike %>% mutate(hr= as_factor(hr))
```
Factor variables can be either numeric or string variables. This makes them useful for statistical modeling.

**Task 2**
```{r}
ggpairs(bike, columns = c(10:13, 16))
```
from the results of the plot, the variable "temp" seems to be best correlated with count.
**Task 3**
```{r}
ggplot(bike,aes(x=hr,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=season,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=holiday,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=mnth,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=weekday,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=workingday,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=weathersit,y=count)) + geom_boxplot() + theme_bw()

```
hr hr does have an affect on count as we can see that the counts are typically higher during midday
season season does have an affect on count, as we can see that count is typically higher in warmer seasons
holiday while we can see than "non-holidays" tend to have higher sales numbers, both relationships have around the same quartiles. holiday does not have a significant affect on count.
mnth mnth has an affect on count. we can see that count is usually higher in the warmer months.
weekday while counts are usually higher mid week, the quartiles seem to remain steady throughout the week. weekday does not have an affect on count.
workingday the quartiles show that there is no real affect on workingday and count as there is not significant change throughout.
weathersit weathersit does have an affect on count. count is typically higher on non-rainy days.
**Task 4**
```{r}
weathersit_simple = recipe(count ~ weathersit, bike) 
#1st df, org df


weathersitlm_model=  
  #2nd df
linear_reg() %>%
set_engine("lm")

weathersitlm_wflow= 
  #3rd df
workflow() %>%
add_model(weathersitlm_model) %>% 
  #2nd df
add_recipe(weathersit_simple)     
#1st df

weathersitlm_fit =                
#4th df
fit(weathersitlm_wflow,bike)    
#3rd df, org df

summary(weathersitlm_fit$fit$fit$fit) 
#4th df

```
with the adjusted r-squared being .02, the model seems to be of good quality.
**Task 5**
```{r}
str(bike)

bike_recipe=recipe(count~season+mnth+hr+holiday+weekday+workingday+weathersit+temp+atemp+hum+windspeed,bike) %>%
  
step_dummy(all_nominal()) %>%

step_center(all_predictors())  %>%
step_scale(all_predictors())

Bike_Ridge_Model=
linear_reg(mixture =  0)%>%
set_engine("glmnet")

ridge_wflow =
workflow() %>%
add_model(Bike_Ridge_Model) %>%
add_recipe(bike_recipe) 

bike_ridge_fit = fit(ridge_wflow,bike)
bike_ridge_fit
plot(bike_ridge_fit$fit$fit$fit$lambda,bike_ridge_fit$fit$fit$fit$dev.ratio)

bike_ridge_fit %>%
pull_workflow_fit() %>%
pluck("fit")

``` 


An appropriate Lambda would be 17 on an R squared value of .6196. This model, or alpha, we can see form the plot that this represents a good regularlization strength.


**Task 6**
```{r}
bike_recipe_lasso=recipe(count~season+mnth+hr+holiday+weekday+workingday+weathersit+temp+atemp+hum+windspeed,bike) %>%

step_dummy(all_nominal()) %>%
step_center(all_predictors())  %>%
step_scale(all_predictors()) 

Bike_Lasso_Model=
linear_reg(mixture = 1) %>%
set_engine("glmnet")
Bike_Lasso_Wflow =
workflow() %>%
add_model(Bike_Lasso_Model) %>%
add_recipe(bike_recipe_lasso)

Bike_Lasso_Model_fit= fit(Bike_Lasso_Wflow,bike)
Bike_Lasso_Model_fit
plot(Bike_Lasso_Model_fit$fit$fit$fit$lambda,Bike_Lasso_Model_fit$fit$fit$fit$dev.ratio)

Bike_Lasso_Model_fit %>%
pull_workflow_fit() %>%
pluck("fit")

bike_ridge_fit %>%
pull_workflow_fit() %>%
pluck("fit")

```
An appropriate Lambda would be 19 on an R squared value of .6185. This model, or lamda, we can see form the plot that this represents a predictor of the model.
