---
title: "Module 3 assignment 2"
author: "Zackery Bradley"
date: "9/8/2021"
output: word_document
---

**Packages**
```{r}
library(e1071)
library(ROCR)
library(tidymodels)
library(tidyverse)
library(glmnet)
library(readr)
parole <- read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 3/parole.csv")
```
install.packages("e1071")
install.packages("ROCR")
library(e1071)
library(ROCR)
library(tidymodels)
library(tidyverse)
library(glmnet)
library(readr)
parole <- read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 3/parole.csv")
**Pre-Assignment tasks**
```{r}
parole = parole %>% mutate(violator = as_factor(violator))  
parole = parole %>% mutate(male = as_factor(male)) %>%
mutate(male = fct_recode(male, "0" = "female", "1" = "male"))

parole = parole %>% mutate(race = as_factor(race)) %>%
mutate(race = fct_recode(race, "0" = "otherwise", "1" = "white")) 

parole = parole %>% mutate(state = as_factor(state)) %>%
mutate(state = fct_recode(state, "1" = "other state", "2" = "Kentucky", "3" = "Louisiana", "4" = "Virginia"))

parole = parole %>% mutate(crime = as_factor(crime)) %>%
mutate(crime = fct_recode(crime, "1" = "other crime", "2" = "larceny", "3" = "drug related", "4" = "driving related"))

parole = parole %>% mutate(multiple.offenses = as_factor(multiple.offenses)) %>%
mutate(multiple.offenses = fct_recode(multiple.offenses, "no" = "otherwise", "1" = "multiple offenses"))
```

**Task 1**
```{r}
set.seed(12345)
parole_split = initial_split(parole, prob = .70, strata = violator)
train = training(parole_split)
test = testing(parole_split)
```
**Task 2**
```{r}
ggplot(train,aes(x=violator, fill = male)) + geom_bar(position = "fill") + theme_bw()
ggplot(train,aes(x=violator, fill = race)) + geom_bar(position = "fill") + theme_bw()
ggplot(train,aes(x=violator, fill = age)) + geom_bar(position = "fill") + theme_bw()
ggplot(train,aes(x=violator, fill = state)) + geom_bar(position = "fill") + theme_bw()
ggplot(train,aes(x=violator, fill = time.served)) + geom_bar(position = "fill") + theme_bw()
ggplot(train,aes(x=violator, fill = max.sentence)) + geom_bar(position = "fill") + theme_bw()
ggplot(train,aes(x=violator, fill = multiple.offenses)) + geom_bar(position = "fill") + theme_bw()
ggplot(train,aes(x=violator, fill = crime)) + geom_bar(position = "fill") + theme_bw()

```
According to the regression, we could get a sense that a parolee would most likely violate his or her parole based on their state and crime. This is sensible because certain crimes typically have longer parole times; thus giving the parolee more time to violate parole. Also, parole varies greatly in states, as one state may have different state laws than the other.
**Task 3**
```{r}
train_model=
logistic_reg(mode = "classification") %>%
set_engine("glm")

train_recipe = recipe(violator ~ state, train) %>%
step_dummy(all_nominal(), - all_outcomes())

train_wf =
workflow() %>%
add_recipe(train_recipe) %>%
add_model(train_model) 
  
train_fit = fit(train_wf, train)
summary(train_fit$fit$fit$fit)
```
I believe the state variable is the most predictive of the variable "violator". I chose this based on the stacked bar chart above,showing a significant difference in parole violations between states. 
**Task 4**
```{r}

train_model=
logistic_reg(mode = "classification") %>%
set_engine("glm")

train_recipe = recipe(violator ~ crime + state, train) %>%
step_dummy(all_nominal(), - all_outcomes())

train_wf =
workflow() %>%
add_recipe(train_recipe) %>%
add_model(train_model) 
  
train_fit2 = fit(train_wf, train)
summary(train_fit$fit$fit$fit)
```
The model seems to be intuitive because the actual AIC value does not disapate too greatly from the residual deviance. the significant factors include states 3 and 4, which are Louisiana and Virginia respectfully. 
**Task 5**
```{r}
train_model=
logistic_reg(mode = "classification") %>%
set_engine("glm")

train_recipe = recipe(violator ~ state + multiple.offenses + race, train) %>%
step_dummy(all_nominal(), - all_outcomes())

train_wf =
workflow() %>%
add_recipe(train_recipe) %>%
add_model(train_model) 
  
train_fit3 = fit(train_wf, train)
summary(train_fit$fit$fit$fit)
```
upon inspection the model, we could find that the model is of pretty good indicator that whether a parolee violates their parole or not does indeed fluctuate based on the offenders state.significant states include: state 3(Louisiana) and state 4 (Virginia). 
**task 6**
```{r}
predictions = predict(train_fit3, train, type = "prob")[2]
head(predictions)

```


**Task 7**
```{r}
ROCRpred = prediction(predictions, train$violator)
ROCRperf = performance(ROCRpred, "tpr", "fpr")
plot(ROCRperf, colorize=TRUE, print.cutoffs.at=seq(0,1,by=0.1), text.adj=c(-0.2,1.7))
```
**Task 8**

```{r}
as.numeric(performance(ROCRpred, "auc")@y.values)

opt.cut = function(perf, pred){
    cut.ind = mapply(FUN=function(x, y, p){
        d = (x - 0)^2 + (y-1)^2
        ind = which(d == min(d))
        c(sensitivity = y[[ind]], specificity = 1-x[[ind]], 
            cutoff = p[[ind]])
    }, perf@x.values, perf@y.values, pred@cutoffs)
}
print(opt.cut(ROCRperf, ROCRpred))

t1 = table(train$violator,predictions > 0.5)
t1
(t1[1,1]+t1[2,2])/nrow(train)

```
the accuracy is displayed as 89.9%, while the sensitivity and specifivity are 0.7586207 and 0.8210291 given a cutoff of 0.1295001 respectively.




**Task 9**

```{r}
t1 = table(train$violator, predictions > 0.3)
t1
(t1[1,1] + t1[2,2]/nrow(train))
```
**Task 10**
```{r}
(410+34)/(410+37+24+34)
#87.9%
```

accuracy of the model is 87.9%.
