---
title: "Module 6 Assignment 1"
author: "Zackery Bradley"
date: "9/21/2021"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
library(naniar)
library(ggplot2)
trucks = trucks <- read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 6/trucks.csv")

```
library(tidyverse)
library(tidymodels)
library(naniar)
trucks = trucks <- read_csv("C:/Users/bradl/OneDrive/Desktop/BAN502/Module 6/trucks.csv")


**Task 1**
```{r}

str(trucks)
summary(trucks)
vis_miss(trucks)

ggplot(trucks, aes(x = Distance, y = Speeding, color = Speeding))+
geom_point()
```
  There seems to be somewhat of a natural cluster in Drivers, as once the traveling distance exceeds around 150 miles, drivers are more inclined to speed.

**Task 2**
```{r}
trucks_cleaned = scale(trucks)
summary(trucks_cleaned)
trucks_cleaned = trucks %>% select(-Driver_ID)
```
```{r}
kmeans_recipe = recipe(~ Distance + Speeding, trucks_cleaned) 

trucks_dummy = kmeans_recipe %>% 
  step_scale(all_numeric()) %>%
  step_center(all_numeric()) 

trucks_dummy = prep(trucks_dummy, trucks) 

trucks_cleaned = bake(trucks_dummy, trucks)
```
**Task 3**
```{r}
set.seed(64)
clusts = 
  tibble(k = 2) %>%
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts
```
```{r}
clusters = 
  clusts %>%
  unnest(cols = c(tidied))

assignments = 
  clusts %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts %>%
  unnest(cols = c(glanced))
```
**plots**
```{r}
p1 = 
  ggplot(assignments, aes(x = Distance, y = Speeding)) +
  geom_point(aes(color = .cluster), alpha = 0.8) + 
  facet_wrap(~ k)
p1
```
The cluster shown seems to be pretty natural. There is one possible outlier at around a distance of .75. Longer distance typically generates a higher probability of speeding.

**Task 4**
```{r}
set.seed(412)
clusts = 
  tibble(k = 1:8) %>%
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts

clusters = 
  clusts %>%
  unnest(cols = c(tidied))

assignments = 
  clusts %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts %>%
  unnest(cols = c(glanced))

p2 = 
  ggplot(assignments, aes(x = Distance, y = Speeding)) +
  geom_point(aes(color = .cluster), alpha = 0.8) + 
  facet_wrap(~ k)
p2




```
**Task 5**
```{r}

trucks_scaled = scale(trucks) 
summary(trucks_scaled)
```


*Create relevant objects** 
```{r}
clusters =
  clusts %>%
  unnest(cols = c(tidied))

assignments = 
  clusts %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts %>%
  unnest(cols = c(glanced))
```

```{r}
ggplot(clusterings, aes(k, tot.withinss)) +
  geom_line() +
  geom_point() + theme_bw()

```
Cluster 4 appears to be the best.

**Task 6**
```{r}
set.seed(64)
clusts = 
  tibble(k = 4) %>%
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts
```
```{r}
clusters = 
  clusts %>%
  unnest(cols = c(tidied))

assignments = 
  clusts %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts %>%
  unnest(cols = c(glanced))
```
**plots**
```{r}
p3 = 
  ggplot(assignments, aes(x = Distance, y = Speeding)) +
  geom_point(aes(color = .cluster), alpha = 0.8) + 
  facet_wrap(~ k)
p3
```
```
Given the optimal cluster, the majority of drivers in cluster 4 maintain safe speeds on long distances.



