---
title: "MOd3Assignment1_Bradley"
author: "Zackery Bradley"
date: "9/7/2021"
output: word_document
---

**Packages**
```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(glmnet)
library(readr)
library(ggcorrplot)
library(MASS)
library(car)
library(lubridate)
library(lmtest)
bike_cleaned_2 <- read_csv("bike_cleaned-2.csv")
```
library(tidyverse)
library(tidymodels)
library(GGally)
library(glmnet)
library(readr)
library(ggcorrplot)
library(MASS)
library(car)
library(lubridate)
library(lmtest)
bike_cleaned_2 <- read_csv("bike_cleaned-2.csv")

**conversions**
```{r}
bike = bike_cleaned_2 %>% mutate(dteday =mdy(dteday)) 
bike = bike %>% mutate(season = as_factor(season))
bike = bike %>% mutate(mnth = as_factor(mnth))
bike = bike %>% mutate(holiday = as_factor(holiday))
bike = bike %>% mutate(weekday = as_factor(weekday))
bike = bike %>% mutate(workingday = as_factor(workingday))
bike = bike %>% mutate(weathersit = as_factor(weathersit))
bike = bike %>% mutate(hr= as_factor(hr))
```
**Task 1**
```{r}
set.seed(1234)
bike_split  = initial_split(bike_cleaned_2, prob = .70, strata = count)
train = training(bike_split)
test = testing(bike_split)

```

**Task 2**
There are 4,347 rows in the test split, and 13,032 rows in the train split.


**Task 3**
```{r}

bike_recipe = recipe(count~season + mnth + hr + holiday + weekday + temp + weathersit, train)

bike_model=
linear_reg() %>%
set_engine("lm")
bike_wflow =
workflow() %>%
add_model(bike_model) %>%
add_recipe(bike_recipe)
bike_fit=
fit(bike_wflow,train)
summary(bike_fit$fit$fit$fit)

```
the adjusted R squared value of .3231 shows a very weak correlation on the model.

**Task 4**
```{r}
predict_train <- bike_fit %>% predict(test) %>%
bind_cols(test) %>%
metrics(truth = count, estimate = .pred)

predict_train$count
ggplot(data = predict_train,aes((.estimate))) +
geom_histogram()
```

**task 5**
The test set r squared value of .3185 compared to the models performance on the training set value of .3231 shows the data is not overly fitted.
