---
output:
  word_document: default
  html_document: default
editor_options: 
  chunk_output_type: inline
---
# **Module 6 -Assignment 1**
## **Bradley Zackery**
### **Lubridate**

```{r}
library(tidyverse)
library(dbplyr)
library(lubridate)
library(readr)
Appointments <- read_csv("C:/Users/bradl/OneDrive/Desktop/MODULE 2/modul 6/Appointments.csv")

```
#==Part 2

#==Question 11-15

# **Working With Dates**

```{r}
Appointments <- Appointments %>%

mutate(ReservationYear='2019') %>%

mutate(ReservationDate = make_date(month=ReservationMonth, day=ReservationDay, year=ReservationYear)) %>%

  mutate(CreationDate = make_date(month=CreationMonth, day=CreationDay, year=CreationYear)) 
  
    Appointments$ReservationSpan <- (Appointments$ReservationDate-Appointments$CreationDate)


```
#==part 3

#==Question 16-22

# **Exploratory Analysis**

```{r}
summary(Appointments)

Appointments$ReservationSpan<- as.numeric(Appointments$ReservationSpan)

summary(Appointments)

  
cor(Appointments$ReservationSpan,Appointments$Show)


ggplot(data = Appointments, aes("show"))+
geom_bar()
```
#a. What is the average time between appointment creation and the actual reservation date? 38.53
#b. What was the max time? 207
#c. What was the min time? 1

#a. Are ReservationSpan and Show highly correlated? No

#a. Based on 0 being “no show” and 1 being “show”, did most people make their appointments? Yes, most people made their appointments.







